Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/metis-language-and-proofs.tex
Numbered all the examples.
Cosmetics.
[ paper ] fixed a typo.

\begin{myexample}
For instance, let us express the problem
$p\, ⊢ ¬  (p ∧ ¬ p) ∨ (q ∧ ¬ q)$
in \TPTP syntax. We begin by declaring the $p$ axiom using the \verb!axiom!
keyword. Later, we include the expected conclusion using the
\verb!conjecture! keyword.

@@

\begin{myexample}

@@

\begin{verbatim}
  fof(subgoal_0, plain, p, inference(strip, [], [goal])).
\end{verbatim}
\end{myexample}

@@

We first present the \strip inference rule since it is the rule that appears
first after each conjecture. The other rules are sorted mainly follow their
level of complexity of their definitions and the formalization presented in
Section~\ref{ssec:emulating-inferences}. Some inference rules depends the
formalizations of other rules. For instance, the \simplify rule and the
\clausify rule  need functions developed for the \canonicalize rule. The
\canonicalize rule needs functions developed in the \resolve section. But the
\resolve rule depends on the \conjunct rule.

% We note a lack of clarity in defining the differences between the rules used in \TSTP derivations and the rules described on the documentation in
% the Metis description~\cite{hurd2003first}.
% These rules are not the same as we expected from the Fig.~\ref{fig:metis-inferences}.

@@

% Finally, \emph{axiom} rule appears in \TSTP derivations by using one of the following rules: \canonicalize, \clausify, \conjunct, or \simplify.
% Then, the last rule remains is \emph{resolve}, it
% appears by the binary rule, \resolve, the version in \Metis of the resolution
% theorem. For a more detailed description of this rules see Section~\ref{sec:proof-reconstruction}.

@@

\caption{\Metis inference rules.}
  \begin{center}
  {\renewcommand{\arraystretch}{1.6}%
    \label{tab:agda-metis-table}
    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}c@{\hspace{2mm}}|}
    \hline
    \textbf{\Metis Rule} & \textbf{Purpose} &\textbf{Theorem}\\ \hline

>>>>

\begin{myexamplenum}
For instance, let us express the problem
$p\, ⊢ ¬  (p ∧ ¬ p) ∨ (q ∧ ¬ q)$
in \TPTP syntax. We begin by declaring the $p$ axiom using the \verb!axiom!
keyword. Later, we include the expected conclusion using the
\verb!conjecture! keyword.

@@

\begin{myexamplenum}

@@

\begin{verbatim}
  fof(subgoal_0, plain, p, inference(strip, [], [goal])).
\end{verbatim}
\end{myexamplenum}

@@

We first present the \strip inference rule since it is the rule that appears
first after each conjecture. The other rules are sorted mainly follow their
level of complexity of their definitions and the formalization presented in
Section~\ref{ssec:emulating-inferences}. Some inference rules depend on the
formalizations of other rules. For instance, the \simplify rule and the
\clausify rule need theorems developed for the \canonicalize rule. The
\canonicalize rule needs theorems developed in the \resolve section. But the
\resolve rule depends on the \conjunct rule.

@@

@@

\caption{\Metis inference rules.}
  \begin{center}
  {\renewcommand{\arraystretch}{1.6}%
    \label{tab:agda-metis-table}
    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}c@{\hspace{2mm}}|}
    \hline
    \textbf{\Metis rule} & \textbf{Purpose} &\textbf{Theorem number}\\ \hline
